\documentclass[10pt]{article}
\usepackage[a4paper, left=0.40in, right=0.40in, top=0.25in, bottom=0.15in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\hyphenation{Some-long-word}

\usepackage{resume}

\begin{document}
	
\begin{center}
	\textbf{\LARGE Mahammad Parvez Salim}\\[0.5ex]
	\href{https://www.findparvez.me/}{https://www.findparvez.me/}\\
	\textscale{1.00}{16100 Space Center boulevard , Houston,TX 77062\\
	
		\Letter\hspace{0.1ex}
	\href{mailto:psalim1992@gmail.com}{psalim1992@gmail.com}
		
		\Mobilefone\hspace{0.1ex} +1 (469) 770-3826}	
\end{center}
\spacedhrule{-1.0ex}{-0.5ex}

\roottitle{SKILLS}

\begin{indentsection}
	\skill{Proficient}{Java,C\#,C,Python,SQL,JavaScript,Spring,Maven, Data Structure and algorithm,OO Design, System Design }
	\skill{Tools}{Eclipse,IntelliJ,Spring Tool Suite,Microsoft SQL Server management Studio, Pycharm, Jupyter Notebook,}
\end{indentsection}
\spacedhrule{0.8ex}{0.0ex}

\roottitle{WORK EXPERIENCE}

\headedsection
{\href{https://www.uhcl.edu/}{University of Houston- Clear Lake}}
{Houston, USA}
{Volunteer Research Assistance}
{\period{March}{2019}{Present}{}}
{\vspace{-2.4ex}
	\begin{circlist}
	    \item  Assisting professor in Software Engineering Modeling and Network Security.
		
	\end{circlist}
}

\headedsection
{\href{https://wpslab.in/}{NJS Web Publishing Systems Private Limited}}
{Hyderabad, India}
{Software Engineer}
{\period{Jan}{2015}{Dec}{2017}}
{\vspace{-2.4ex}
	\begin{circlist}
	 
	    \item  Implemented new features to JSF application utilizing  JDBC for backend data access.
		\item Designing the application modules, base classes and utility classes using core Java.
		\item Used MySQL database for SQL scripts,stored procedures, functions.
		\item Developed interactive and user friendly web pages using JSP, CSS, HTML, JavaScript.
		\item Helped developing RESTful Web Services, using Spring
		
	\end{circlist}
}

\headedsection
{\href{https://www.globsyn.com/}{Globsyn Group}}
{Kolkata, IN}
{Globsyn Finishing School, Summer Trainee}
{\period{July}{2013}{Sep}{2013}}
{\vspace{-2.4ex}
    \begin{circlist}	
	    \item Built an E-commerce website using C\# and ASP.Net.
	    \item A website which can handle every kind of E-Commerce activity from user and admin side.
	    \item 160 hours of training on Object oriented programming language and ASP.Net.
    \end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}
\roottitle{PUBLICATION}

\headedsectionthree
{Stock Market Prediction}{{August. }{2016}}
{\href{https://dl.acm.org/citation.cfm?id=3305804/}{Hasanuzzaman, Mohammed, Wai Leung Sze, Mahammad Parvez Salim, and Gaël Dias. "Collective future orientation and stock markets."\newline In Proceedings of the Twenty-second European Conference on Artificial Intelligence,\newline pp. 1616-1617. IOS Press,2016}}
{\vspace{-2.4ex}
    \begin{circlist}
        \item Acceptance rate was 27\%
    \end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}
\roottitle{ACADEMIC PROJECTS}

\headedsectionthree
{Fully Functional Online Dating Website}{\period{August}{2019}{September}{2019}}
{\href{}{\vspace{-2ex}}}
{\vspace{-2.4ex}
    \begin{circlist}
         \item  Used Java  to create a web-based application with Eclipse IDE.
	    \item For database management, worked with MySQL..
	    \item Designed user interface using HTML5 and CSS3.
	    \item Implemented features such as send and receive messages, view user profiles, add friends by sending requests,accept
requests and view notifications.
    \end{circlist}
}
\headedsectionthree
{Unauthenticated Transaction Detection in dell.com  }{\period{September}{2019}{December}{2019}}
{\href{}{\vspace{-2ex}}}
{\vspace{-2.4ex}
    \begin{circlist}
        \item Performed data collection using JavaScript.
        \item Created Web API using ASP .NET MVC to store the data into the database.
        \item Created the rules to detect the unauthenticated transaction within the same session using T-SQL.
    \end{circlist}
}
\headedsectionthree
{Los Angeles County Metropolitan Transportation Authority Demand and Operation Forecasting}{\period{September}{2019}{October}{2019}}
{\href{}{\vspace{-2ex}}}
{\vspace{-2.4ex}
    \begin{circlist}
	    \item Implemented seasonal ARIMA algorithm to forecast bike demand with 70\% of accuracy .
	    \item classifying the customers with Decision Tree, Naive Bayse, and Logistic regression with 65\% of accuracy.
	    \item Creating a predictive model for predicting the usage rate for a given station, on a given day and hour using Random Forest Regressor and Decision Tree Regressor with 70\% of accuracy.
	    \item Clustered the stations  based on the number of bikes they rent – using KMeans algorithm.
    \end{circlist}
}
\headedsectionthree
{Dimension Modelling using Dillard's Data Set}{\period{March}{2018}{April}{2018}}
{\href{}{\vspace{-2ex}}}
{\vspace{-2.4ex}
    \begin{circlist}
	    \item Developed an multidimensional cube with OLAP.
	    \item Designed schema and made reports for sales and marketing for the data.
	    \item Built a dashboard and created visualization using IBM Watson Analytics.
    \end{circlist}
}

\spacedhrule{0.8ex}{0.0ex}
\roottitle{EDUCATION}

\headedsection
{University Of Houston-Clear Lake}
{Houston, TX}
{Master of Computer Information System }
{\period{January}{2018}{December}{2019}}

\headedsection
{West Bengal University of Technology}
{Kolkata, India}
{Bachelors of Computer Science and Engineering}
{\period{August}{2011}{August}{2015}}


\end{document}
